---
title: "HW1_nh2706"
output: github_document
---

```{r, message = FALSE, echo=FALSE}
library(tidyverse)
```

# Section 1

## Loading Data

Downloading the a package containing the `penguins` dataset

```{r}
data("penguins", package = "palmerpenguins")
```

## Data Summary
Presenting the data to you (*shows the chunk but not the output*):

```{r, eval=FALSE}
skimr::skim(penguins)
```

The summary above shows the following key information:

*   The dataset is `r nrow(penguins)` rows long and `r ncol(penguins)` columns wide
*   8 total variables:
    *   5 numeric:
        *   bill_length_mm: mean = `r round(mean(na.omit(penguins$bill_length_mm)),2)` 
        *   bill_depth_mm: mean = `r round(mean(na.omit(penguins$bill_depth_mm)),2)`
        *   **flipper_length_mm: mean = `r round(mean(na.omit(penguins$flipper_length_mm)),2)`**
        *   body_mass_g: mean = `r round(mean(na.omit(penguins$body_mass_g)),2)`
        *   year: mean = `r round(mean(penguins$year),2)`
    * 3 factor:
        *   species (3 factors)
        *   island (3 factors)
        *   sex (3 factors)

## Scatterplot with bill_length and flipper_length

Creating a scatterplot of `bill_length_mm` and `flipper_length_mm`, using the different species to colorcode the individual points.

```{r, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

Subsequently, exporting the scatterplot to the project directory as a **PDF**

```{r, eval=FALSE}
ggsave("scatterplot.pdf")
```


# Section 2

## Data Frame Creation

Using `tible`, we are now creating a datafram with the following specs:

*   **random_vec** = random sample of size 10 from a standard Normal distribution
*   **logical_vec** = logical vector indicating whether elements of the sample are greater than 0
*   **character_vec** = character vector of length 10
*   **factor_vec** = factor vector of length 10, with 3 different factor “levels”

```{r}
hw_frame =
  tibble(
    random_vec = rnorm(n = 10),
    logical_vec = random_vec > 0,
    character_vec = c(sample(LETTERS, 10, replace = TRUE)),
    factor_vec = factor(cut(random_vec,3,labels = c('Low','Medium','High')))
  )
```

## Calculating the mean of each variable

When trying to take the mean of each variable, the result is the following (*rounded to the nearest tenth*). :

*   **random_vec** = `r round(mean(hw_frame$random_vec),2)`. This works, because it is a numeric variable.
*   **logical_vec** = `r mean(hw_frame$logical_vec)`. This works, because it is a TRUE/FALSE variable, which can be converted to numeric values (TRUE = 1 and FALSE = 0).
*   **character_vec** = No result because the variable is not numerical.
*   **factor_vec** = No result because the variable is not numerical.

## Converting character and factor variables to numeric variables

Given that the mean of the character and factor variables could not be calculating, the next step is to convert those variables to a numeric variable.

To do so, I am creating three new variables `Num_logical_vec`, `Num_character_vec`, `Num_factor_vec` (Note: **(1)** *shows the chunk but not the output* **(2)** *Could have used `pull` function, but instead opted for extraction operator `$`*):

```{r, eval=FALSE}
Num_logical_vec = as.numeric(hw_frame$logical_vec)
Num_character_vec = as.numeric(hw_frame$character_vec)
Num_factor_vec = as.numeric(hw_frame$factor_vec)
```


The result of this is that the logical and factor variable can be converted to a numeric variable based on  logic (TRUE/FALSE & 3 Categories). However, the character variable is filled with NA, since there is no logic to convert to numeric values.

# END OF HW1