---
title: "HW1_nh2706"
output: github_document
---

```{r, message = FALSE, echo=FALSE}
library(tidyverse)
```

# Section 1

## Loading Data

Downloading the a package containing the `penguins` dataset

```{r}
data("penguins", package = "palmerpenguins")
```

## Data Summary
Presenting the data to you:

`r skimr::skim(penguins)`

The summary above shows  that the size of the dataset is `r nrow(penguins)` rows long and `r ncol(penguins)` columns wide. 

The mean flipper length within the dataset is `r round(mean(na.omit(penguins$flipper_length_mm)),2)` millimeters.

## Scatterplot with bill_length and flipper_length

Creating a scatterplot of `bill_length_mm` and `flipper_length_mm`, using the different species to colorcode the individual points.

```{r, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color=species)) + geom_point()
```

Subsequently, exporting the scatterplot to the project directory as a **PDF**

```{r, warning==FALSE}
ggsave("scatterplot.pdf")
```


# Section 2

## Data Frame Creation

Using `tible`, we are now creating a datafram with the required specs.

```{r}
hw_frame=
  tibble(
    random=rnorm(n=10),
    logical=random>0,
  )
```





